Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-03 neurips-20/cvx-flats.tex
working on the lemma

\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
\newcommand{\iden}{\mathrm{iden}}
\newcommand{\Var}{\mathrm{Var}}

@@

\begin{lemma}\label{lem:set-valued-prop-flats}
	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
\end{lemma}
\begin{proof}

\end{proof}

>>>>

\newcommand{\ellbar}{\underline{\ell}}
\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
\newcommand{\iden}{\mathrm{iden}}
\newcommand{\Var}{\mathrm{Var}}

@@

A hyperplane weakly separates two sets if its two closed halfspaces respectively contain the two sets.
\begin{lemma}\label{lem:intersect-levelsets}
  If $\gamma: \simplex \toto \R$ is an elicitable property, then for any pair of predictions $r \neq r' \in \R$, there is a hyperplane $H = \{p : v \cdot p = 0\}$ that weakly separates both $\gamma_r$ and $\gamma_{r'}$ with $\gamma_r \cap \gamma_{r'} \subseteq H$.
\end{lemma}
\begin{proof}
  Because $\gamma$ is elicitable, its level sets are closed convex bounded sets.\bo{cite}
  Note that if the intersection $\gamma_r \cap \gamma_{r'} = \emptyset$, then the separating hyperplane theorem already gives an $H$ that strictly separates the two sets, in particular, $\gamma_r \cap \gamma_{r'}$.

  Each level set is a set of $p$ having the same subgradient of the Bayes risk of $\ell$, e.g. for some $s$, we have $\gamma_r = \{ p : s \in \partial \ellbar (p) \}$.\bo{cite}
  So $\gamma_r \cap \gamma_{r'} = \{ p : s,s' \in \partial \ellbar(p)\}$, for some $s,s'$.
  \bo{TO DO}
\end{proof}

\begin{lemma}\label{lem:set-valued-prop-flats}
	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
	Then for any flat $F$ containing $p$, $F \cap \simplex \subseteq \gamma_r \iff F \cap \simplex \subseteq \gamma_{r'}$.
\end{lemma}
\begin{proof}
  First, we claim \botodo{separate into another lemma?} that $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
  Let it be parameterized by the unit vector $v \in \reals^{\Y}$, where $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0 \}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0\}$, and $q \in \gamma_r \cap \gamma_{r'} \implies v \cdot q = 0$.

  Now, we prove the equivalent claim $F \cap \simplex \subsetneq \gamma_r \iff F \cap \simplex \subsetneq \gamma_{r'}$.
  Suppose $F \cap \simplex$ has a point $q$ not in $\gamma_r$.
  If $v \cdot q < 0$, then $q$ is already not in $\gamma_{r'}$, QED.
  Otherwise, we claim that $p - \epsilon (q-p) \in F \cap \simplex$ for small enough $\epsilon$.
  Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\simplex$ follows because $p \in \relint\simplex$.
  But $v \cdot (p - \epsilon (q-p)) = -\epsilon (v \cdot q) < 0$, so $q$ is not in $\gamma_{r'}$, QED.
\end{proof}
